Spin canonical rings of log stacky curves

### 2015-07-14 curves-write-up/arXiv versions/spin-cring-arXiv-v2.tex
add arXiv-v2 files, close missing parens

\ssec{Saturation}
\label{ssec:g-0-saturation}
First, we present the saturations of the log spin canonical divisor
for all cases where $g = 0$ and $\delta = 0$ (recall Definition
~\ref{defn:sat} in Table ~\ref{table:g-0-sat}. The saturations can
be computed using Riemann-Roch. By classifying the saturations of
all signatures, we can determine the base cases on which we can
apply inductive lemmas from Section ~\ref{sec:induction}. Note that
the saturations of log spin canonical divisors only depend on the
signature here. In Table ~\ref{table:g-0-sat}, exceptional cases
are listed first and generic cases follow.

\begin{table}
\begin{tabular}
	{| c | c || c |}
	\hline
	Signature $\sigma$ & Condition & Saturation \\
	\hline
	\hline

@@

>>>>

\ssec{Saturation}
\label{ssec:g-0-saturation}
\begin{table}
\begin{tabular}
	{| c | c || c |}
	\hline
	Signature $\sigma$ & Condition & Saturation \\
	\hline
	\hline

@@

First, we present the saturations of the log spin canonical divisor
(recall Definition ~\ref{defn:sat}) for all cases where $g = 0$ and
$\delta = 0$ in Table ~\ref{table:g-0-sat}. The saturations can
be computed using Riemann-Roch. By classifying the saturations of
all signatures, we can determine the base cases on which we can
apply inductive lemmas from Section ~\ref{sec:induction}. Note that
the saturations of log spin canonical divisors only depend on the
signature here. In Table ~\ref{table:g-0-sat}, exceptional cases
are listed first and generic cases follow.
